---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# coronaDetails

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/zahradm/coronaDetails.svg?branch=master)](https://travis-ci.com/zahradm/coronaDetails)
<!-- badges: end -->

The goal of coronaDetails is to plot of coronaviruce and updating data

## Installation


The development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("zahradm/coronaDetails")
```
## Example

The newdata() function get data from Johns Hopkins University and output is  a csv file that contains number of confirmed and death cases 




```{r pressure, echo = FALSE}

```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!
